Create data sets for modeling

### 2016-07-14 portfolio/analysis/3-createData_linear_modeling.Rmd
Divide some gears by taxonomic groups

>>>>

cfecnew$gear_group[cfecnew$p_spec == "Salmon" & 
  cfecnew$gear_group == "drift gillnet"] <- "drift gillnet salmon"
cfecnew$gear_group[cfecnew$p_spec == "Salmon" & 
  cfecnew$gear_group == "purse seine"] <- "purse seine salmon"
cfecnew$gear_group[(cfecnew$p_spec == "Sablefish" | cfecnew$p_spec == "Halibut") & 
  cfecnew$gear_group == "pot gear"] <- "pot gear sablefish/halibut"
cfecnew$gear_group[(cfecnew$p_spec == "Sablefish" | cfecnew$p_spec == "Halibut") & 
  cfecnew$gear_group == "longline under 60"] <- "longline under 60 sablefish/halibut"
cfecnew$gear_group[(cfecnew$p_spec == "Sablefish" | cfecnew$p_spec == "Halibut") & 
  cfecnew$gear_group == "longline over 60"] <- "longline over 60 sablefish/halibut"
cfecnew$gear_group[(cfecnew$p_spec == "Sablefish" | cfecnew$p_spec == "Halibut") & 
  cfecnew$gear_group == "longline over 90"] <- "longline over 90 sablefish/halibut"
